Reconstructing the Lensing Mass in the Universe \\ from Photometric Catalog Data

### 2012-10-30 doc/paper-lcr.tex
done halos section...

\begin{figure*}
\includegraphics[width=\textwidth]{figs/viewofalightcone.eps}
\caption[magcut]{Four different views of a slightly over-dense \MS line
of sight, with a $\kappa$ of 0.03. 
{\it Top row, left:} The positions of galaxies projected on the sky. The area
of the circles is proportional to observed $i$-band flux; the brightest
object shown has an $i$ magnitude of 17.7. 
{\it Top row, centre:} The angular sizes of halos projected on the sky.
Red and blue regions lie within the NFW scale radius and virial radius
of each halo, respectively. There are essentially no empty lightcones. 
{\it Top row, right:} The individual $\kappa$ contributions of
each halo, assuming the \citet{BMO} profile and the \citet{Neto2007}
mass-concentration relation. Comparison of
this panel and the centre panel reveals the relative importance of
proximity to the line of sight.
{\it Bottom:} A view along the redshift axis, showing only halos with
$|x|<0.3$ arcmin. The area of the points is proportional to each halo's
mass: the most massive halo shown has $1.6\times10^{12}\Msun$. The
optical axis is shown by the dashed line, while the dotted lines mark
the lens and source planes for a B1608-like strong lens.}
\label{fig:lightcone}
\end{figure*}

@@

\section{The Millenium Simulation}
\label{sec:MS}

@@

\subsection{Mock Galaxy Catalogs}
\label{sec:MS:mocks}

Our goal is to recover the ``true'' convergence defined in the previous
sub-section, via an inference that takes a catalog of galaxy positions
and properties as data. We construct such catalogs by selecting all \MS
galaxies within a circular aperture of a given angular radius centred on
the line of sight position, with apparent $i$-band magnitude brighter
than a given limit. The parent catalog, from \citet{HilbertEtal2011},
contains galaxy positions and magnitudes, all of which include lensing
effects (deflections and magnifications). We also have access to the
underlying galaxy halo masses and redshifts, which we will use to
calibrate the reconstruction, and also to explore any sources of bias
and scatter. Since the true convergence is that of only the dark matter,
we focus on reconstructing the dark matter halos alone. Our model for
doing this is outlined in the next section.

@@

For real lines of sight, we would like to estimate the external convergence given all
data available. Typically this data is in the form of a photometric galaxy
catalog, containing positions, brightnesses, colours, and possibly spectra for each galaxy in the
field of the lens, down to some magnitude
limit. Since we can not observe the surface mass density of each halo
directy, we need some way of estimating
the mass of each halo in the catalog, so that we can compute its
contribution to the total $\kappax$ along the line of sight. This mass assignment recipe will be uncertain, but
can be calibrated with cosmological simulations.

Transforming the photometometric galaxy catalogue into a  catalogue of
halo masses, positions, and redshifts, will enable us to attempt a
reconstruction of the convergence induced by every halo near a line of sight.
This is the subject of Section \ref{subsec:halos}. We also need to account for
the mass in the Universe that is not associated with the galaxies we can see
-- this is the subject of Section \ref{subsec:voids}.

@@

Cosmological dark matter simulations have shown that dark matter
halos are well approximated by NFW profiles \citep{NFW}, with a density
profile given by
\be\label{eq:rhonfw}
\rho(r) = 
\frac{\rho_0}{\left(r/r_{s}\right)
\left(1+r/r_{s}\right)^{2}},
\ee
where $r_{s}$ is a characteristic radius of the cluster, representing where
the density slope transitions from $r^{-1}$ to $r^{-3}$. This radius is related
to the virial radius of the halo by $r_{s}~=~r_{200}/c$, where $r_{200}$ is the radius at 
which 
\be
\rho(r_{200}) = 200\rho_{{\mathrm{crit}}}(z), \text{ where } \rho_{\mathrm{crit}}(z) \equiv \frac{3H^{2}(z)}{8\pi G}
\ee
and $c$ is the concentration parameter, which can be estimated from the halo's mass,
using a mass--concentration relation. Typically more massive halos are less concentrated,
but there is some scatter; we use the relation of \citet{Neto2007} to estimate $c$
from the mass enclosed within $r_{200}$, which we denote as $M_{200}$. We find our results do not change if the \citet{MaccioEtal2008} Mass--concencetration relation is used instead. The best fit relation of \citet{Neto2007} is given by
\be
c_{200} = 4.67 (M_{200}/10^{14} h^{-1} \Msun)^{-0.11}.
\ee
$\rho_0$ is calculated from the critical density and concentration parameter:
\be
\rho_0 = \rho_{\mathrm{crit}}(z)\frac{200}{3}\frac{c^{3}}{\ln(1+c)-c/(1+c)}.
\ee

Unphysically, if one integrates the density profile of an NFW profile, the total mass is divergent.
Similarly, if the universe is homogeneously populated with NFW halos, the projected surface mass along any
line of sight will also be divergant\footnote{At large radius, $\Sigma_{\rm
nfw} \propto R^{-2}$, but the differential number of halos centred within an
annulus of width $\dee R$ is given by $\dee N_{\rm annulus} \propto R \dee R$,
so  $\Sigma_{\rm total} \propto \int_{0}^{\infty} R^{-1} \dee R$, which
diverges logarithmically}. Since infinite mass is unphysical, the profile must
be truncated at some point. Several truncation profiles have been suggested \citep[e.g][]{BMO}, but beyond several virial radii, the amount of matter associated with a halo is likely to be low. In this work we assume the truncated NFW profile of \citet{BMO}
\be\label{eq:bmoprofile}
\rho(r) = 
\frac{\rho_{\rm NFW} (r)}{1+\left(r/r_{t}\right)^2},
\ee
which is the same as the NFW profile in the limit that the truncation radius, $r_t$ goes to infinity. We use a truncation radius of five times the virial radius, but our results are robust for any choice of $r_t>2 \times r_{200}$.

The projected surface mass density $\Sigma(r)$ for this mass profile is derived in \citet{BMO}. Each halo in our catalogue then contributes to the line of sight convergence by
\be
\label{eq:kappai}
\kappa_i =\Sigma_{i}/\Sigma_{\mathrm{cr}}(z_i,\zs),
\ee
where the critical surface density was defined in \Eref{eq:sigcrit}.
Following the first order approximation of \citet{HilbertEtal2009}
outlined in \Sref{sec:MS} above, we compute 
the total convergence from all the halos along the line
of sight using
\be 
\label{eq:kappasummu}
\kappah = \sum_{i} \kappa_i.
\ee

To estimate a halo's contribution to $\kappah$ we must first know the halo's mass.
For the calibration sightlines of the \MS halo masses are known, but for 
real lines of sight this can only be infered from the stellar masses of the
galaxies within a halo. We use the relation of \citet{BehrooziEtal2010} to generate 
halo masses from stellar masses; the details of this proceedure are outlined in
Appendix \ref{appendix:MSMH}.

Given an uncertain halo mass and redshift for a halo we draw a sample mass and redshift and use Equation \ref{eq:kappai} to generate a sample $\kappa_i$; this can be done for all the halos along the line of sight and summed to give a sample $\kappah$; repeatedly applying this proceedure allows us to characterize $\pr(\kappah)$. However we found that our proceedure for estimating halo masses induces long tails in the $\pr(\kappah)$ distribution that are not present in the global $\kappah$ distribution given perfect knowledge of halo mass and redshift, to correct for this we use the global $\kappah$ distribution as a prior on $\pr(\kappah)$.

@@

The proceedure outlined in Section \ref{subsec:halos} allows us to estimate 
the convergence due to halos given observations of mass, redshift and position
$\pr(\kappah|\mathcal{D})$, but what we are interested in is the total convergence
along the line of sight $\pr(\kappa|\mathcal{D})$. We can obtain this by
considering the expression:
\begin{equation}
\Pr(\kappa|\mathcal{D}) = \int \dee\kappah 
   \Pr(\kappa|\kappah) \Pr(\kappah|\mathcal{D})
\label{eq:kappaconv}   
\end{equation}
The first term in the integrand relates the summed convergence due to model
halos, $\kappah$, to the true convergence, $\kappa$. In the Millenium
Simulation catalogs, we can compute $\kappah$ for each
selected line of sight and combine multiple lines of sight to calculate $\Pr(\kappa|\kappah)$.

@@

In order to test the reconstruction proceedure outlined in Section
\ref{sec:model}, we now apply it to mock galaxy catalogs generated in
regions on the sky around lines of sight with known
$\kappa$ in the Millenium Simulation.

@@

Since voids are not included in the halo model approximation $\kappah$
is a biased estimator of $\kappa$, but this can be calibrated for useing
the proceedure of Section \ref{subsec:voids}. Taking the reconstructed
$\kappah$ for $1\times 10^{5}$ lines of sight we form the joint
distribution, P$(\kappa,\kappah)$ and marginalize over P$(\kappah)$ to
give P($\kappa$). We define the bias as the difference between the
expectation value of $\kappa$ and the known true value of $\kapparay$
for each Line of sight and we define the reconstruction width,
$\sigma_{\kappa}$,as half the width of the interval containing the
central $68\%$ of the probability P($\kappax$). From $1\times 10^{4}$
reconstructed lines of sight we find the the bias to have mean of
$-9.5\times 10^{-6}$ and a mean reconstruction width of 0.0132 which is
roughly 1.8 times smaller than the width of the global P$(\kappax)$. We
find that our $\kappa$ distributions are consistent with the global
$\kappa$ distribution; Figure \ref{fig:globaldist} shows that sampling
from $\pr(\kappa)$ for 100000 lines of sight is very similar to the
global $\pr(\kappa)$. Given perfect knowledge of halo mass and redshift,
the calibration proceedure provides an unbiased estimate of $\kappa$
that is $\sim$2 times as precise than using the global $\pr(\kappa)$.

@@

\section{Applying the Halo Model approximation to mock catalogs}
\label{sec:obsMstar+z}

@@

Given an uncertain stellar mass and redshift it is possible to infer a
halo mass using the stellar mass--halo mass relation of
\citet{BehrooziEtal2010}. This proceedure requires an inversion of the
relation given in \citet{BehrooziEtal2010} and correctly inverting the
relation's uncertainties requires care: the proceedure we use to do this
is given in Appendix \ref{appendix:MSMH}. By drawing sample halo masses
and redshifts, we can infer a sample $\kappah$ using the proceedure of
Section \ref{sec:model}; repeatedly drawing samples allows us to
estimate P$(\kappah)$ for each reconstructed line of sight.

@@

\begin{figure}
\includegraphics[width=\columnwidth]{figs/Width.eps}
\caption[magcut]{The widths of the infered P$(\kappah|\mathcal{D})$ for $10^5$ lines of sight given different amounts of data. Blue assumes a spectroscopic redshift for every halo with $i<26$, purple assumes a spectroscopic redshift for every halo with $i<23$ and every within 1 arcminute and $i<24$, cyan assumes a spectroscopic redshift for every halo with $i<22$ and green assumes that no objects in the field have a spectroscopic redshift}
\label{fig:reconwidths}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{figs/Widthvshilberrt.eps}
\caption[magcut]{Width of the infered P$(\kappah|\mathcal{D})$ verses the true $\kappa$ along a line of sight. Blue assumes a spectroscopic redshift for every halo, whilst green assumes no spectroscopic redshifts. The width of the infered P$(\kappah)$ increases with $\kappa$. If correctly reconstructed, the lowest density lines of sight can provide the most precise measurement of the time delay distance.}
\label{fig:widthsvsH}
\end{figure}

@@

Inferring the stellar mass of a galaxy from its magnitude and colours requires an estimate of how far away the galaxy is; without a spectroscopic redshift the the infered stellar mass is less precise. However, obtaining photometry has much lower observational cost; over the next few years several large area photometric surveys will reach 24th magnitude \citep{EUCLID,LSST}, these will provide sufficient data to reconstruct lines of sight {\it without} additional observations. In principle the photometric redshift is correlated with the infered stellar mass, however we do not model this effect since the convergence from the outskirts of an individual halo is only weakly dependant on redshift at fixed mass: the redshift error is small effect on the recovered $\pr(\kappa)$ when compared to the effect of uncertain stellar masses.  With only photometric redshifts the uncertainty on $\sum\kapparec^{\rm halos}$ is much larger than the spectrocopic case and this propogates into a broader $\pr(\kappa)$, although the photometric reconstruction still typically produces a 1.4 fold improvement compared to the precision of the global P($\kappa$).

@@

\section{Testing for Systematic errors}
\label{sec:biases}
\begin{figure*}
\includegraphics[width=\textwidth]{figs/biasplots.eps}
\caption[magcut]{Estimating $\kappa-\kappa_{\rm true}$ from subsets of
lenses. By subtracting the true (ray-traced) convergence from the
infered P($\kappa$) for each line of sight we are left with a PDF that
should be estimating zero, these can be multiplied together for multiple
lines of sight to test for a possible bias. These plots show the
expectation value of $\prod_{i=1}^N \pr_i(\kappa-\kappa_{\rm true})$ -
deviations from zero can be seen as a bias. The solid, dashed and dotted
lines are for combining 20, 5 and 2 lenses respectively. Green lines are
from multiplying P($\kappa$) infered from photometry alone, whilst red
lines are from multiplying P($\kappa$) infered from photometry and a
spectroscopic redshift for all halos with $i<23$ and all halos within 1
arcminute and $i<24$. The left most plot shows randomly selected lines
of sight. The central plot shows sight lines randomly selected from the
third of lines whose P($\kappa$) is most tightly constrained. The right
hand plot shows only lines of sight with external shear of 0.03 or
greater.}
\label{fig:biasplots}
\end{figure*}

Whilst it is good to reconstruct $\kappa$ precisely it is vital that $\kappa$ is reconstructed accurately. A precise, inaccurate $\kappa$ estimator is worse than useless for cosmology. We test the accuracy of our reconstructed $\pr(\kappa)$ in the following way: for each line of sight we shift the reconstructed $\pr(\kappa)$ by the line of sight's raytraced $\kappa$ to give $\pr(\kappa-\kapparay)$. Since the $\pr(\kappa-\kapparay)$ for each line of sight is an independant estimator of zero, the PDFs can be combined according to

@@

\subsubsection{Selecting only high shear lines of sight}
\todo{phil}{Write up why lenses are likely to be gamma biased}
\notes{The uncertainties from modeling a strong lens system depends on
the comfiguration of the source images. With only two point images ofthe
source the lens slope and mass are degenerate; the mass-slope
degeneracy\citep[need citation][Saha?]{mass-slope degeneracy}. Where lensed arcs or
four point images are present the mass-slope degeneracy can be broken
and cosmology can be extracted, \citep{Suyu2012a}. The detectability of
arcs depend on the source, but the presence of four images (so called
quads) depend on the shear of the lens model - a high shear is needed to
produce a quad. The shear is almost certainly dominated by the lens
model itself, but it is possible that quads are biased towards high
external shear.}

By selecting only lines of sight with an external shear of $\gamma>0.03$ we can test the effect of shear selection. We find that in all cases $\kappa$ is underestimated at the $\sim$0.01 level. Part of this effect is mitigated if only the lines of sight with both $\gamma>0.03$ and sharp $\pr(\kappax)$ are used but biases at the $\sim$0.005 level remain. Since our model does not include shear constraints it is not surprising that selecting based on shear can induce a bias. A more sophisticated model that includes the shear recovered from the lens modelling may not be susceptable to this bias. The toy model of this section ($\gamma>0.03$) is likely to be a much stronger selection than reality, but it is worth noting that the reconstruction proceedure will be biased if lens selection functions are extreme and unaccounted.

@@

\item It is very rare for halos further than 2 arcminutes to make a
significant contribution to $\kappa$. We also found that including halos
whose host galaxy is less luminous than $i=24$ does not significantly improve
our reconstruction proceedure. A photometric survey to this depth of a
4$\times$4 arcminute patch around the lens would approach the limiting
uncertainties of our simple reconstruction recipe, and yield a 
$\pr(\kappa)$ that has, on average, a width of 0.016 --
1.5 times less broad than the global $\pr(\kappa)$.

@@

External convergence is not the only uncertainty in time delay cosmology,
but for systems like B1608 it is the dominant one. For most lines
of sight it is likely that lens modelling induces uncertainties at the
$\sim$3 percent level, which far exceeds the typical $\kappa$ uncertainties
after applying our reconstruction proceedure. By using our method to
reconstruct lines of sight and select which lense are followed-up, the
uncertainties due to line of sight convergence will become a sub-dominant 
source of error.

@@

To estimate the convergence caused by a halo we need to know its mass; how can 
halo mass be infered from a noisy estimate of the stellar mass $\Mstarobs$
of a galaxy at redshift $z$. We seek the posterior
PDF $\Pr(\Mhalo|\Mstarobs,z)$, which can be expanded as follows:

>>>>

\begin{figure*}
\includegraphics[width=\textwidth]{figs/viewofalightcone.eps}
\caption[magcut]{Four different views of a slightly over-dense \MS line
of sight, with a $\kappa$ of 0.03. 
{\it Top row, left:} The positions of galaxies projected on the sky. The area
of the circles is proportional to observed $i$-band flux; the brightest
object shown has an $i$ magnitude of 17.7. 
{\it Top row, centre:} The angular sizes of halos projected on the sky.
Red and blue regions lie within the NFW scale radius and virial radius
of each halo, respectively. There are essentially no empty lightcones. 
{\it Top row, right:} The individual $\kappa$ contributions of
each halo, assuming a \citet{BMO} profile and the \citet{Neto2007}
mass-concentration relation. Comparison of
this panel and the centre panel reveals the relative importance of
proximity to the line of sight.
{\it Bottom:} A view along the redshift axis, showing only halos with
$|x|<0.3$ arcmin. The area of the points is proportional to each halo's
mass: the most massive halo shown has $1.6\times10^{12}\Msun$. The
optical axis is shown by the dashed line, while the dotted lines mark
the lens and source planes for a B1608-like strong lens.}
\label{fig:lightcone}
\end{figure*}

@@

\section{The Millennium Simulation}
\label{sec:MS}

@@

\subsection{Mock Photometric Galaxy Catalogs}
\label{sec:MS:mocks}

We construct mock photometric galaxy catalogs by selecting all \MS
galaxies within a circular aperture of a given angular radius centred on
the line of sight position, with apparent $i$-band magnitude brighter
than a given limit. The parent catalog, from \citet{HilbertEtal2011},
contains galaxy positions and magnitudes, all of which include lensing
effects (deflections and magnifications). We also have access to the
underlying galaxy halo masses and redshifts, which we will use to
calibrate the reconstruction, and also to explore any sources of bias
and scatter. Since the true convergence is that of only the dark matter,
we focus on reconstructing the dark matter halos alone. Our model for
doing this is outlined in the next section.

@@

One of the goals of this paper is to define a method for estimating the
convergence at any point on the sky, given a   catalog of observed
galaxy positions and properties. Typically this could be a  photometric
galaxy catalog, containing positions, brightnesses, colours, and
possibly stellar masses and redshifts for each galaxy in the field of
the lens, down to some magnitude limit. Since we cannot observe the
surface mass density of each halo directy, we need some way of
estimating the mass of each halo in the catalog, so that we can compute
its contribution to the total $\kappa$ along the line of sight \citep[as
in \eg][]{GunnarssonEtal2006,WongEtal2011}. This mass assignment recipe
will be uncertain, but can be calibrated with cosmological simulations.

Transforming an observed photometometric galaxy catalogue into a 
catalogue of halo masses, positions, and redshifts, will enable us to
attempt a reconstruction of the convergence induced by every halo near a
line of sight. This is the subject of Section \ref{subsec:halos}. We
also need to account for the mass in the Universe that is not associated
with the galaxies we can see -- this is the subject of Section
\ref{subsec:voids}.

@@

Cosmological dark matter simulations have shown that dark matter
halos are well-approximated by NFW profiles \citep{NFW}, with a density
profile given by
\be\label{eq:rhonfw}
\rho(r) = 
\frac{\rho_0}{\left(r/r_{s}\right)
\left(1+r/r_{s}\right)^{2}},
\ee
where $r_{s}$ is a characteristic radius of the cluster, representing where
the density slope transitions from $r^{-1}$ to $r^{-3}$. This radius is related
to the virial radius of the halo by $r_{s}~=~r_{200}/c$, where $r_{200}$ is the radius at 
which 
\be
\rho(r_{200}) = 200\rho_{{\mathrm{crit}}}(z), \text{ where } \rho_{\mathrm{crit}}(z) \equiv \frac{3H^{2}(z)}{8\pi G}
\ee
and $c$ is the concentration parameter, which can be estimated from the halo's mass,
using a mass--concentration relation. Typically more massive halos are less concentrated,
but there is some scatter; we use the relation of \citet{Neto2007} to estimate $c$
from the mass enclosed within $r_{200}$, which we denote as $M_{200}$. We find our results do not change if the \citet{MaccioEtal2008} Mass--concencetration relation is used instead. The best fit relation of \citet{Neto2007} is given by
\be
c_{200} = 4.67 (M_{200}/10^{14} h^{-1} \Msun)^{-0.11}.
\ee
\todo{Tom}{Add sentence about scatter!}

$\rho_0$ is calculated from the critical density and concentration parameter:
\be
\rho_0 = \rho_{\mathrm{crit}}(z)\frac{200}{3}\frac{c^{3}}{\ln(1+c)-c/(1+c)}.
\ee

If one integrates the density profile of an NFW profile out to infinite
radius, the total mass diverges. Similarly, if the universe is
homogeneously populated with NFW halos, the projected surface mass along
any line of sight will also be divergant.\footnote{At large radius,
$\Sigma_{\rm nfw} \propto R^{-2}$, but the differential number of halos
centred within an annulus of width $\dee R$ is given by $\dee N_{\rm
annulus} \propto R \dee R$, so  $\Sigma_{\rm total} \propto
\int_{0}^{\infty} R^{-1} \dee R$, which diverges logarithmically} Since
infinite mass is unphysical, the profile must be truncated at some
point. Several truncation profiles have been suggested
\citep[e.g][]{BMO}, but beyond several virial radii, the amount of
matter associated with a halo is likely to be low. In this work we
assume the truncated NFW profile
\be\label{eq:bmoprofile}
\rho(r) = 
\frac{\rho_{\rm NFW} (r)}{1+\left(r/r_{t}\right)^2},
\ee
which is the same as the NFW profile in the limit that the truncation
radius, $r_t$ goes to infinity. We use a truncation radius of five times
the virial radius, but our results are robust for any choice of $r_t>2
\times r_{200}$. The formula for the projected surface mass density 
$\Sigma(D_{od}\theta)$ for this
mass profile is given in \citet{BMO}.

Each halo in our catalogue then contributes to
the line of sight convergence by
\be
\label{eq:kappai}
\kappa_i =\Sigma_{i}/\Sigma_{\mathrm{cr}}(z_i,\zs),
\ee
where the critical surface density was defined in \Eref{eq:sigcrit}.
Following the first order approximation of \citet{HilbertEtal2009}
outlined in \Sref{sec:MS} above, we compute 
the total convergence from all the halos along the line
of sight using
\be 
\label{eq:kappasummu}
\kappah = \sum_{i} \kappa_i.
\ee

To estimate a halo's contribution to $\kappah$ we must first know the
halo's mass. For the sightlines of the \MS, halo masses are
known, but for  real lines of sight the halo masses have to be \infered
from whatever data is available. 
In this work we investigate the use of the empirical stellar mass --
halo mass relation for this purpose. The primary advantage of this
approach is that it is a simple, ``one size fits all'' relation that can
be applied regardless of the stellar mass observed. We discuss
additional observables that could be used to improve the precision of
the halo mass inference in \Sref{sec:discuss} below.

We use the relation of \citet{BehrooziEtal2010} to infer halo masses
from stellar masses; the details of this \proceedure are outlined in 
\Aref{appendix:MSMH}. Given an uncertain stellar mass and redshift for
each galaxy in the  catalog, we draw a sample halo mass from the PDF
that describes this uncertainty  (\Eref{eq:mhalo-mstar})  and use
\Eref{eq:kappai} to compute its contribution to the convergence,
$\kappa_i$; this can be done for all the halos along the line of sight
and summed to give a sample value of $\kappah$;  repeatedly applying
this \proceedure allows us to build up a histogram of $\kappah$ values
consistent with the data, and hence characterize $\pr(\kappah|\data)$.

This PDF contains a hidden assumption of an uninformative prior PDF for
$kappah$ -- in the case of infinitely poorly measured stellar masses and
redshifts, $\pr(\kappah|\data)$ will have very long tails that we do not
belive to exist. The resolution of this is to apply an additional prior
on $\kappah$, given by the global underlying $\kappah$ distribution from
the simulation, $\pr(\kappah)$. In the limiting  case of very poor
photometric data, $\pr(\kappah|\data)$ then defaults to this
distribution. \todo{All}{Discuss this. It ties us to the simulation --
but is not unreasonable. Is the argument about poor data valid? Tom?}

@@

The \proceedure outlined in Section \ref{subsec:halos} allows us to estimate 
the convergence due to halos given observations of mass, redshift and position
$\pr(\kappah|\mathcal{D})$, but what we are interested in is the total convergence
along the line of sight $\pr(\kappa|\mathcal{D})$. We can obtain this by
considering the expression:
\begin{equation}
\Pr(\kappa|\mathcal{D}) = \int \dee\kappah 
   \Pr(\kappa|\kappah) \Pr(\kappah|\mathcal{D})
\label{eq:kappaconv}   
\end{equation}
The first term in the integrand relates the summed convergence due to model
halos, $\kappah$, to the true convergence, $\kappa$. In the Millenium
Simulation catalogs, we can compute $\kappah$ for each
selected line of sight and combine multiple lines of sight to calculate $\Pr(\kappa|\kappah)$.

@@

In order to test the reconstruction \proceedure outlined in Section
\ref{sec:model}, we now apply it to mock galaxy catalogs generated in
regions on the sky around lines of sight with known
$\kappa$ in the Millenium Simulation.

@@

Since voids are not included in the halo model approximation $\kappah$
is a biased estimator of $\kappa$, but this can be calibrated for useing
the \proceedure of Section \ref{subsec:voids}. Taking the reconstructed
$\kappah$ for $1\times 10^{5}$ lines of sight we form the joint
distribution, P$(\kappa,\kappah)$ and marginalize over P$(\kappah)$ to
give P($\kappa$). We define the bias as the difference between the
expectation value of $\kappa$ and the known true value of $\kapparay$
for each Line of sight and we define the reconstruction width,
$\sigma_{\kappa}$,as half the width of the interval containing the
central $68\%$ of the probability P($\kappax$). From $1\times 10^{4}$
reconstructed lines of sight we find the the bias to have mean of
$-9.5\times 10^{-6}$ and a mean reconstruction width of 0.0132 which is
roughly 1.8 times smaller than the width of the global P$(\kappax)$. We
find that our $\kappa$ distributions are consistent with the global
$\kappa$ distribution; Figure \ref{fig:globaldist} shows that sampling
from $\pr(\kappa)$ for 100000 lines of sight is very similar to the
global $\pr(\kappa)$. Given perfect knowledge of halo mass and redshift,
the calibration \proceedure provides an unbiased estimate of $\kappa$
that is $\sim$2 times as precise than using the global $\pr(\kappa)$.

@@

\section{Testing the Halo Model Reconstruction on Mock Galaxy Catalogs}
\label{sec:obsMstar+z}

@@

Given an uncertain stellar mass and redshift it is possible to infer a
halo mass using the stellar mass--halo mass relation of
\citet{BehrooziEtal2010}. This \proceedure requires an inversion of the
relation given in \citet{BehrooziEtal2010} and correctly inverting the
relation's uncertainties requires care: the \proceedure we use to do this
is given in Appendix \ref{appendix:MSMH}. By drawing sample halo masses
and redshifts, we can infer a sample $\kappah$ using the \proceedure of
Section \ref{sec:model}; repeatedly drawing samples allows us to
estimate P$(\kappah)$ for each reconstructed line of sight.

@@

\begin{figure}
\includegraphics[width=\columnwidth]{figs/Width.eps}
\caption[magcut]{The widths of the \infered P$(\kappah|\mathcal{D})$ for $10^5$ lines of sight given different amounts of data. Blue assumes a spectroscopic redshift for every halo with $i<26$, purple assumes a spectroscopic redshift for every halo with $i<23$ and every within 1 arcminute and $i<24$, cyan assumes a spectroscopic redshift for every halo with $i<22$ and green assumes that no objects in the field have a spectroscopic redshift}
\label{fig:reconwidths}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{figs/Widthvshilberrt.eps}
\caption[magcut]{Width of the \infered P$(\kappah|\mathcal{D})$ verses
the true $\kappa$ along a line of sight. Blue assumes a spectroscopic
redshift for every halo, whilst green assumes no spectroscopic
redshifts. The width of the \infered P$(\kappah)$ increases with $\kappa$. If correctly reconstructed, the lowest density lines of sight can provide the most precise measurement of the time delay distance.}
\label{fig:widthsvsH}
\end{figure}

@@

Inferring the stellar mass of a galaxy from its magnitude and colours requires an estimate of how far away the galaxy is; without a spectroscopic redshift the the \infered stellar mass is less precise. However, obtaining photometry has much lower observational cost; over the next few years several large area photometric surveys will reach 24th magnitude \citep{EUCLID,LSST}, these will provide sufficient data to reconstruct lines of sight {\it without} additional observations. In principle the photometric redshift is correlated with the \infered stellar mass, however we do not model this effect since the convergence from the outskirts of an individual halo is only weakly dependant on redshift at fixed mass: the redshift error is small effect on the recovered $\pr(\kappa)$ when compared to the effect of uncertain stellar masses.  With only photometric redshifts the uncertainty on $\sum\kapparec^{\rm halos}$ is much larger than the spectrocopic case and this propogates into a broader $\pr(\kappa)$, although the photometric reconstruction still typically produces a 1.4 fold improvement compared to the precision of the global P($\kappa$).

@@

\section{Testing for Systematic errors}
\label{sec:biases}
\begin{figure*}
\includegraphics[width=\textwidth]{figs/biasplots.eps}
\caption[magcut]{Estimating $\kappa-\kappa_{\rm true}$ from subsets of
lenses. By subtracting the true (ray-traced) convergence from the
infered P($\kappa$) for each line of sight we are left with a PDF that
should be estimating zero, these can be multiplied together for multiple
lines of sight to test for a possible bias. These plots show the
expectation value of $\prod_{i=1}^N \pr_i(\kappa-\kappa_{\rm true})$ -
deviations from zero can be seen as a bias. The solid, dashed and dotted
lines are for combining 20, 5 and 2 lenses respectively. Green lines are
from multiplying P($\kappa$) \infered from photometry alone, whilst red
lines are from multiplying P($\kappa$) \infered from photometry and a
spectroscopic redshift for all halos with $i<23$ and all halos within 1
arcminute and $i<24$. The left most plot shows randomly selected lines
of sight. The central plot shows sight lines randomly selected from the
third of lines whose P($\kappa$) is most tightly constrained. The right
hand plot shows only lines of sight with external shear of 0.03 or
greater.}
\label{fig:biasplots}
\end{figure*}

Whilst it is good to reconstruct $\kappa$ precisely it is vital that
$\kappa$ is reconstructed accurately. A precise, inaccurate $\kappa$
estimator is worse than useless for cosmology. We test the accuracy of
our reconstructed $\pr(\kappa)$ in the following way: for each line of
sight we shift the reconstructed $\pr(\kappa)$ by the line of sight's
raytraced $\kappa$ to give $\pr(\kappa-\kapparay)$. Since the
$\pr(\kappa-\kapparay)$ for each line of sight is an \independant estimator of zero, the PDFs can be combined according to

@@

\subsubsection{Selecting only high shear lines of sight}

\todo{phil}{Write up why lenses are likely to be gamma biased}

\notes{The uncertainties from modeling a strong lens system depends on
the comfiguration of the source images. With only two point images ofthe
source the lens slope and mass are degenerate; the mass-slope
degeneracy\citep[need citation][Saha?]{mass-slope degeneracy}. Where
lensed arcs or four point images are present the mass-slope degeneracy
can be broken and cosmology can be extracted, \citep{Suyu2012a}. The
detectability of arcs depend on the source, but the presence of four
images (so called quads) depend on the shear of the lens model - a high
shear is needed to produce a quad. The shear is almost certainly
dominated by the lens model itself, but it is possible that quads are
biased towards high external shear.}

By selecting only lines of sight with an external shear of $\gamma>0.03$ we can test the effect of shear selection. We find that in all cases $\kappa$ is underestimated at the $\sim$0.01 level. Part of this effect is mitigated if only the lines of sight with both $\gamma>0.03$ and sharp $\pr(\kappax)$ are used but biases at the $\sim$0.005 level remain. Since our model does not include shear constraints it is not surprising that selecting based on shear can induce a bias. A more sophisticated model that includes the shear recovered from the lens modelling may not be susceptable to this bias. The toy model of this section ($\gamma>0.03$) is likely to be a much stronger selection than reality, but it is worth noting that the reconstruction \proceedure will be biased if lens selection functions are extreme and unaccounted.

@@

\item It is very rare for halos further than 2 arcminutes to make a
significant contribution to $\kappa$. We also found that including halos
whose host galaxy is less luminous than $i=24$ does not significantly improve
our reconstruction \proceedure. A photometric survey to this depth of a
4$\times$4 arcminute patch around the lens would approach the limiting
uncertainties of our simple reconstruction recipe, and yield a 
$\pr(\kappa)$ that has, on average, a width of 0.016 --
1.5 times less broad than the global $\pr(\kappa)$.

@@

External convergence is not the only uncertainty in time delay cosmology,
but for systems like B1608 it is the dominant one. For most lines
of sight it is likely that lens modelling induces uncertainties at the
$\sim$3 percent level, which far exceeds the typical $\kappa$ uncertainties
after applying our reconstruction \proceedure. By using our method to
reconstruct lines of sight and select which lense are followed-up, the
uncertainties due to line of sight convergence will become a sub-dominant 
source of error.

@@

To estimate the convergence caused by a halo we need to know its mass; how can 
halo mass be \infered from a noisy estimate of the stellar mass $\Mstarobs$
of a galaxy at redshift $z$. We seek the posterior
PDF $\Pr(\Mhalo|\Mstarobs,z)$, which can be expanded as follows:
